30 years of privacy research for the masses \& \newline 15 years of decentralization attempts

### 2014-03-13 paper.tex
completed incentive part

		\subsection{Incentives in decentralized systems}
		As described in section \ref{ss:tor_disadvantages} people are using more bandwidth than that they donate. There are multiple proposals \cite{dingledine2010building, jansen13lira} to introduce incentives into Tor. If one would also have to build an incentive system into a decentralized system, they would have to find a way to manage the ratings of each client in the network, in such a way that they cannot be falsely modified. In other words the incentive data has to be accurate and reliable. Besides the integrity of the data, also the traffic it generates on the network should have minimal impact.\\
		Rahman \cite{rahman2009survey} ........

@@

	\section{Conclusion}
		We come to the conclusion that there is no complete decentralized system that provides the full functionality and security that Tor offers today. While there is a lot of research on decentralized systems, only a few are actually implemented. The systems that do exist such as X and Y (hier deze noemen aan de hand van de tabel) are getting things right, yet they often lack or have poor implementations on other aspects.\\
While Tor also still has a lot to improve on, further research and development is needed to improve the current decentralized systems and develop a decentralized system that matches Tor's current standards.

>>>>

		\subsection{Incentives in decentralized systems}
		As described in section \ref{ss:tor_disadvantages} people are using more bandwidth than that they donate. There are multiple proposals \cite{dingledine2010building, jansen13lira} to introduce incentives into Tor. If one would also have to build an incentive system into a decentralized system, they would have to find a way to manage the ratings of each client in the network, in such a way that they cannot be falsely modified. In other words the incentive data has to be accurate and reliable. Besides the integrity of the data, also the traffic it generates on the network should have minimal impact.\\

		Rahman \cite{rahman2009survey} proposes several options to build in incentives in a peer-to-peer network. The first thing that is described is the so called \emph{Warm-glow Model}. In this model determines the percentage of free-rides based on the probabilistic population distribution. If the percentage is above a certain threshold, the system will show signs of diminishing marginal returns.\\

		The second proposal is using monetary schemes. While it is not exemplified a lot, the main idea is to use a virtual currency as incentive. The problems with this approach are the scalability and the hidden costs of this service.\\

		The third proposal is \emph{Reciprocity-Based Schemes}. Using this approach a peer maintains a behavior history of other peers in the network. These schemes can be based on two somewhat reciprocities: direct reciprocity or indirect reciprocity. The formal are more suitable for longer relationships between peers. The latter is more scalable but they rely on third party and must handle trust issues themselves.

@@

	\section{Conclusion}
		In this technical report we introduced Tor and explained how Tor works and which components define a Tor network. Furthermore we looked at the main disadvantages and problems Tor currently has. We then made a bridge to decentralized systems. We first explained which problems one might face when decentralizing a system such as Tor. The next section shows which systems currently have a decentralized structure and/or mechanism. These systems are then compared to each other with their pros and cons.\\

		From this table we come to the conclusion that there is no complete decentralized system that provides the full functionality and security that Tor offers today. While there is a lot of research on decentralized systems, there is not a system yet that can compete with Tor. The systems that do exist such as Tarzan, Torsk and Gnutella are getting things right, yet they often lack functionality such as anonymity or XXXXXX.\\

While Tor also still has a lot to improve on, further research and development is needed to improve the current decentralized systems and develop a decentralized system that matches Tor's current standards.
